%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Senior Software Engineer} % Job title
    {Monedo Holding GmbH (formerly Kreditech Holdings SSL GmbH)} % Organization
    {Hamburg, Germany} % Location
    {Aug. 2017 - Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Acted as a co-Tech Lead for the past 1 year for the Underwriting team.}
        \item {Developed the Scoring Engine using Akka Streams that executes the decision tree from a score-card, consuming from and writing data to RabbitMQ topics.}
        \item {Built the Orchestrator component using Akka HTTP which orchestrates the dynamic selection and invocation of Data Science machine-learning models based on the assigned weight of the model, and generates the offer/rejection.}
        \item {Developed several external service connectors that are invoked by the Scoring Engine to collect data of the customer using Akka HTTP.}
        \item {Worked on the DataWriter and DataReader components developed using Akka Streams and Akka HTTP that streamlines the operations to MongoDB.}
        \item {Deployed a centralized monitoring environment (Kibana Visualization, New Relic) which gathers system metrics as well as docker run-time metrics.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {R\&D Engineer} % Job title
    {Nokia Networks} % Organization
    {Bangalore, India} % Location
    {Apr. 2015 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented REST APIs for data handling and the support of configuring WiFi-AP in the Cloud-based Wireless LAN Controller.}
        \item {Helped build and maintain the features of the customer-facing UI web components.}
        \item {Built dynamic reporting charts for the Cloud-WLAN controller administrator that shows the real-time metrics of the attached WiFi-APs.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineering Analyst} % Job title
    {Accenture Services Pvt. Ltd.} % Organization
    {Bangalore, India} % Location
    {Jul. 2012 - Apr. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Helped build and maintain features of the backend event-based Vehicle Tracking application built on message parsing.}
        \item {Designed REST APIs that facilitates the administrator users to send communication to any vehicle in their fleet and get their real-time status.}
        \item {Built the ETL pipeline over Pentaho Reporting suite.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
